---
title: "What to do to stop the inceasing deforestation in western Madagascar dry forests?"
bibliography: bib/biblio.bib
csl: bib/elsevier-harvard.csl
output: 
  html_document:
    fig_caption: yes
---

```{r load_data}
load("menabe.rda")
```

#### Ghislain Vieilledent<sup>*,1,2</sup>, Clovis Grinand<sup>3</sup>, Miguel Pedrono<sup>2</sup>, Tsiky Rabetrano<sup>4</sup>, Bruno Rakotoarivelo<sup>5</sup>, Fety A. Rakotomalala<sup>3</sup>, Frédéric Achard<sup>1</sup> and Dimby Razafimpahanana<sup>4</sup>

(*) /Email: ghislain.vieilledent@cirad.fr, /Phone: +39.329.457.2273

1. Joint Research Center of the European Commission, Institute for Environment and Sustainability, I-21027 Ispra (VA), ITALY
2. Cirad, UPR Forêts et Sociétés, F-34398 Montpellier, FRANCE
3. ETC Terra, F-75016 Paris, FRANCE
4. Wildlife Conservation Society, 101 Antananarivo, MADAGASCAR
5. Office National de l'Environnement, 101 Antananarivo, MADAGASCAR

## Context

### Field mission to central Menabe

- Projects: Roadless Forests (JRC) and BioSceneMada (Cirad)
- Sites: Kirindy-Mitea national park (KMNP) and Menabe-Antimena new protected area (MANAP)
- Dates: from 4th to 12th of June 2016
- Participants: Clovis Grinand (1), Miguel Pedrono (2), Tsiky Rabetrano (3), Bruno Rakotoarivelo (4), Fety A. Rakotomalala (1), Dimby Razafimpahanana (3) and Ghislain Vieilledent (2,5)
- E-mails: c.grinand@etcterra.org, miguel.pedrono@cirad.fr, tsikyrabetrano@gmail.com, rbruno@pnae.mg, f.rakotomalala@etcterra.org, dimby@wcs.org, ghislain.vieilledent@cirad.fr
- Institutions: (1) ETC Terra, (2) Cirad, (3) Wildlife Conservation Society, (4) Office National de l'Environnement, (5) Joint Research Center of the European Commission

### Program

- Saturday 04th: Antananarivo -- Morondava
- Sunday 05th: Morondava -- Belo-sur-Mer. Contact with Stefan, keeper at Madagascar National Park (MNP) office
- Monday 06th: deforestation from cyclone and uncontrolled fires in KMNP and savannas
- Thuesday 07th: visit to the dunes and lake in KMNP and illegal logging. Discussion with KMNP conservation director
- Wednesday 08th: avorted trial to see the "Sentier des baobabs". Discussion at the Ecolodge du Menabe with Roland Eve from WWF
- Thursday 09th: Belo-sur-Mer -- Morondava -- Marofandilia. Meeting with Direction Régionale des Eaux et Forêt (DREF) in Morondava
- Friday 10th: deforestation from _"hatsake"_ around Kirindy-Village and Lambokely. Contact with EPFL PhD student. Visit of the de Haulme concession 
- Saturday 11th: Naturalist observations around Bedo lake
- Sunday 12th: Marofandilia -- Antananarivo

### Contacts

- Linjasoa Rakotomalala, linjanantenaina@yahoo.fr, PhD Student at ESSA-Forêt Antananarivo and EPFL Lausanne
- Mamy Rakotobenandrasana, ratsimedmond@gmail.com, Chef du volet conservation recherche (CVCR) à MNP pour les parcs de Kirindy-Mitea et Menabe-Antimena
- Roland Eve, reve@wwf.mg, Landscape Planning and Management advisor and Chief Technical advisor WWF MDCO
- Mme Cynthia, Directrice par intérim, Direction Régionale des Eaux et Forêts, région Menabe
- Rebecca Lewis, rjlewis@austin.utexas.edu, Associate Professor, Antrhopology, University of Texas, Director of the Ankoasikafa research station in KMNP. Study of Verreaux’s sifaka (_Propithecus verreauxi_)
- Tahina Riniavo, tahinariniavo@gmail.com, NGO Fanamby, Responsable conservation Menabe-Antimena

## Summary

1. Madagascar is recognized for both its unparrallel biodiversity, concentrated mainly in tropical forests, and its high level of threat which is associated in particular to deforestation. Madagascar population, which is rapidly increasing, is one of the poorest in the world and people rely strongly on forests for their livelihood. Since the end of the colonization (in 1960), many effort have been done to fight poverty and curb deforestation through implementing large development and conservation programs. Despite these efforts, Madagascar remains in the top countries with the highest deforestation rates and the forest cover, particularly in the western dry ecoregion, is rapidly decreasing. 

3. To try to explain why it is so difficult to stop deforestation in Madagascar, we analyzed further the deforestation process in two dry forest areas in the central Menabe (western Madagascar) around two protected areas, the Kirindy-Mitea national park and the Menabe-Antimena new protected area. We derived historical deforestation maps for these two areas from Landsat satellite images on the period 1990-2000-2010-2014. We validated these maps and identified the main causes of deforestation with field verification points and through household and stakeholder surveys. We then established a map of the future deforestation on the period 2010-2050 assuming a business-as-usual scenario.

4. We showed that deforestation had recently increased in the two study areas, with about 2.35%.yr<sup>-1</sup> of deforestation on the period 2010-2014 compared to 0.85%.yr<sup>-1</sup> on the period 2000-2010. We identified two major causes of deforestation, the first one being illegal slash-and-burn agriculture for the cultivation of peanut and corn as cash crops, the second one being accidental and uncontrolled forest fires after cyclonic events due to antrhopogenic fires in nearby grasslands to obtain flush of green pasture for livestock. Agents from institutions in charge of the management of the protected areas do not have the mean to inforce law against deforestation. Slash-and-burn agriculture intensified recently due to the settlement or migrants following climate-induced famines in southern Madagascar. Money earned by farmers from peanut and corn productions is used to invest into zebu cows. Peanut production is exported outside Madagascar and a large part of the corn production is used to brew the national beers. These activities benefit to several intermediaries, some of who having political responsabilities, which underlies a conflict of interest in the application of the law against deforestation. 

5. _Conclusions:_ In the absence of an efficient strategy to stop deforestation, we expect that half of the forest present in 2000 will have disappeared before 2050. Forest loss, apart from biodiversity loss and climate-change global issues, will be at the expense of local population. Contrary to what is commonly accepted, deforestation in western Madagascar is not associated to agriculture for autoconsumption. International pressure should be put on the Malagasy government to apply in the first place the law of the environmental code and make use of repressive measures to stop deforestation. Of course, these measures must be accompagnied by incentive measures, through for example agricultural development programs, to offer alternatives to deforestation when necessary.

## 1. Introduction

### 1.1 State of the art

- Madagascar has long been recognized as a biodiversity hotspot highly threatened by deforestation
- Many actions have been implemented to curb deforestation in the country
    - Increase of the protected areas over 10% of the country total area
    - Large investment in development programs (number of NGOs in Madagascar and amout of money for agricultural development and conservation)
    - World Bank with the Environmental Program, USAID, AFD-FFEM, KFW

### 1.2 Knowledge gap

- Nonetheless, deforestation seems to remain very high in Madagascar and has recently increase in intensity despite all the conservation and development measures.
- Why such initiatives are failing and what could be the solution to stop deforestation?
- Is the recent deforestation attributable to external causes, independant of anthropogenic activities, such as climate change?
- Is it really possible to stop deforestation in Madagascar?

### 1.3 Objectives

- To try to answer these questions, we studied the intensity and the causes of deforestation in two protected areas located in western Madagascar and aiming at protecting the dry forest and its unique biodiversity. 

## 2. Materials and Methods

### 2.1 Historical deforestation maps

We derived 30m cloud-free forest maps for Madagascar for the years 1990, 2000, 2010 and 2014 combining the 1990 and 2000 forest maps by @Harper2007 and the 2000-2014 tree percent cover map by @Hansen2013. On Harper's map, ~200,000 ha clouds are present over the ~4.2 million ha moist forest ecoregion (4.8% of clouds). To remove these clouds, we used the 2000 cloud-free tree percent cover map provided by @Hansen2013 (also at 30~m resolution) and we chose a threshold of 75% of tree cover to decide whether to replace cloud pixels with forest or non-forest pixels [@Achard2014]. We thus obtained a cloud-free year 2000 forest map for Madagascar. From this map, using tree cover loss data from 2000 to 2014 by @Hansen2013, we obtained cloud-free forest maps in 2010 and 2014 at 30~m resolution. Finally, we corrected the cloudy 1990 Harper forest map assuming that if forest was present in 2000, it was also present in 1990. Doing so, all clouds were removed and we obtained a cloud-free 1990 forest map for Madagascar. These maps are freely available at http:/bioscenemada.net/forestmaps. We then used these national maps for our regional study around the Kirindy-Mitea national park (E: 43.67555, W: 44.35067, S: -21.36469, N: -20.50137, in decimal degrees) and the Menabe-Antimena new protected area (E: 44.20934, W: 44.8185, S: -20.3644, N: -19.55838, in decimal degrees). Field work was conducting during a ten days mission in June 2016 to verify the presence of the recent (2000-2010-2014) patches of deforestation in the two study areas. We validated the deforestation maps on this period and identified the main causes of deforestation in the two study areas. 

### 2.2 Deforestation model

Following @Vieilledent2013, we considered two processes for modelling deforestation, a first process describing the intensity of deforestation (number of hectares of forest deforested each year) and a second process describing the location of the deforestation (spatial probability of deforestation). For the intensity of deforestation, we computed an historical mean at the national level on the period 1990-2010 from the Madagascar forest maps. We obtained a mean deforestation intensity of 75000 ha.yr<sup>-1</sup>. For the location of the deforestation, we estimated the parameters $\beta$ of a Binomial logistic regression linking the spatial probability of deforestation $\theta_i$ for forest pixel $i$ to a set of spatial explicative factors $X_i$ computed at the pixel level. To account for unexplained spatial variation in the probability of deforestation, we added a spatial random effect $\rho_{j(i)}$ at the level of the 10km resolution cell $j$ including the pixel $i$: $\text{logit}(\theta_i)=X_i\beta+\rho_{j(i)}$. To account for spatial autocorrelation, these spatial random effects were structured with a conditional autoregressive (CAR) model [@Besag1991] where $\rho_j$ depends on the values of $\rho_{j^{\prime}}$ for the neighbouring cells $j^{\prime}$. We used the deforestation data on the period 2000-2010 to fit the model. We used altitude, distance to forest edge, distance to main town, distance to main road, inclusion into a protected area and distance to past deforestation (period 1990-2000) as spatial explicative factors of the probability of deforestation [@Vieilledent2013]. These factors describe the accessibility, the land policy and the historical deforestation of the forest. Model parameters where estimated in a Bayesian framework using the function `hSDM.binomial.iCAR()` from the hSDM `R` package [@Vieilledent2014]. The 10km spatial random effect estimates were interpolated at 1km using a bilinear interpolation. Using the results of the statistical model, we derived a deforestation probability map at 30m resolution for the year 2010 for Madagascar. To forecast the forest cover in 2050 for Madagascar, we removed the 2010 forest pixels with the highest probability of deforestation following a deforestation intensity of 75000 ha.yr<sup>-1</sup> at the national level. The forest map for the year 2050 is freely available at http:/bioscenemada.net/forestmaps and was used for our regional study.

### 2.3 Surveys

During a ten days period in June 2016, we conducted surveys among farmers and environmental stakeholders (Table 1) around the Kirindy-Mitea national park and the Menabe-Antimena new protected area. The objectives of the surveys were first to identify the causes of the deforestation and second to assess the efficiency of the conservation actions implemented by the institution in charge of the management of the protected area, either the non-governmental organisation _"Fanamby"_" for the Menabe-Antimena new protected area or Madagascar National Park for the Kirindy-Mitea national park. Surveys were qualitative and included non-directive questions (no "yes-or-no" questions).

| Id | Type              | Name | Institution     | Position                                        | Date | Duration |
|----|-------------------|------|-----------------|-------------------------------------------------|------|----------|
| 1 | Migrant and farmer | Farmer 1 | Kirindy village | Chief of a family with a woman and eight children | 10/06 | 1h30 |
| 2 | Woman | Woman 1 | Kirindy village | Woman of farmer living in the Kirindy village | 10/06 | 30min |
| 4 | Migrants and farmers | Farmers 2 and 3 | Lambokely | Two family chiefs with women and children | 10/06 | 1h |
| 5 | Administration | Chief 1 | Lambokely | Fokontany chief | 10/06  | 30min |
| 8 | Government representative  |  Mme Cynthia | DREF Menabe | Acting director of the Direction Régionale des Eaux et Forêt | 09/06 | 1h |
| 6 | National Parks | Mamy Rakotobenandrasana | MNP | Director of the conservation program for KMNP | 07/06 | 1h30 |
| 7 | Environmental NGO | Roland Eve | WWF | Landscape Planning and Management advisor for KMNP | 08/06 | 1h |
| 9 | Environmental NGO | Tahina Riniavo | Fanamby | Director of the conservation program for MANAP | 10/06 | 30min |

Table 1: **List of surveys conducted among farmers and environmental stakeholders**. Surveys were conducted around the Kirindy-Mitea national park and the Menabe-Antimena new protected area. The _"Fokontany"_ is a Malagasy term defining an administrative territory under the level of the township. In Madagascar, the management of the protected areas are under the responsability of Madagascar National Parks (MNP) or delegated to an environmental Non-Governmental Organisation (such as the NGO Fanamby for Menabe-Antimena New Protected Areas). 

## 3. Results

### 3.1 Historical deforestation

We estimated that 3960 ha and 3295 ha of forest have disappeared annually on the period 2010-2014 in the study areas around the Kirindy-Mitea national park and the Menabe-Antimena new protected area, respectively. This represent annual deforestation rates of about 2.35%.yr<sup>-1</sup>. The annual deforestation has more than doubled on the period 2010-2014 compared to the period 2000-2010, with an annual deforestation rate on this period of about 0.85%.yr<sup>-1</sup> (Table 3). In the study area around the Kirindy-Mitea national park, mosaic deforestation associated to slash-and-burn agriculture occured outside the protected area, showing a relative effectiveness of the protected area to prevent deforestation (Fig. 2a, label A). Much larger patches of deforestation have been observed on the period 2010-2014 on the east part of the protected area associated to uncontrolled fires after cyclone events (Fig. 2a, label B). Dispersed and small-scale deforestation has also been observed in the northern and western part of the park associated to illegal logging activities (Fig. 2a, label B). In the Menabe-Antimena new protected area, large patches of deforestation were surprisingly not associated to uncontrolled fires but to slash-and-burn agriculture. Most of the deforestation occured around the Kirindy and Lambokely villages and at the south of Belo-sur-Tsiribihina (Fig. 3a).

### 3.2 Causes of deforestation

#### 3.2.1 Slash-and-burn agriculture, uncontrolled fires and illegal logging

We identified three causes of deforestation in the study area around the Kirindy-Mitea national park (Fig. 1). Slash-and-burn agriculture (also know as _"hatsake"_) for corn crops was identified as the main cause of deforestation in several areas at the periphery of the protected area (Fig. 1a, label A). Inside the protected area, uncontrolled fires were identified as the main cause of deforestation (Fig. 1a, label B). People repeatedly set fire on former grasslands (_"bozake"_) outside the protected area to obtain flush of green pasture for their livestock. When uncontrolled, fires can spread on large areas of the forest and cross the boundaries of the protected area. Illegal logging was also identify as one major cause of deforestation in Kirindy-Mitea (Fig. 1a, label C). Timbers are mainly used for construction and sold in local markets in Belo-sur-Mer and Morondava. 

In the study area around the Menabe-Antimena new protected area, the main cause of deforestation was the slash-and-burn agriculture for peanut and corn crop. Peanut is cultivated as cash crop and is transformed into peanut oil. A part of the production is at the destination of the national market but most of it is exported outside Madagascar, mainly for the Chinese market (Fig. 3). Corn is cultivated for auto-consumption and as cash crop. The production of corn is at the destination of the national market and is used in particular to brew national beers, such as the Three Horse Beer (THB) by the Malagasy company Star (bought in 2011 by the French company Castel) which is made from both barley and corn (Fig. 4). Peanut and corn are sold by farmers to resellers at the price of 7000 Malagasy francs (MGF) (equivalent to 1400 Malagasy ariary, MGA) and 2000 MGF (400 MGA) per kilo, respectively. For 2016, the production for a household was of 1.6 tonnes (T) of peanut and 2.5 T of corn, thus providing a relatively high annual income of about 3.24 millions MGA compared to the median household income of 1013 USD or 2.02 millions MGA (data aggregated from household surveys on the period 2006-2012 by The Gallup Organization, we used the USD-MGA mean change rate on the period 2006-2012: 1 USD = 1998 MGA). With the money earned from the sale of the corn and peanut harvest, farmers invest in buying zebu cows (_"omby"_). Buying zebu cow is a way for farmers of saving money such as a bank would do it. In Madagascar, zebu cows represent status, wealth, and cultural identity [@Hobbs2016]. People's diet in the Menabe region is significantly different from people's diet in the highlands which heavily relies on rice. In the Menabe region, rural people eat mainly manioc, yams and corn [@Falola2015]. Notably, the main purpose of the slash-and-burn agriculture is not to obtain food for auto-consumption and food-security but to cultivate cash crop in order to invest in livestock. 

Climate-change could indirectly be identified as a cause of deforestation in the central Menabe region. It is now largely recognized that climate change can increase the number of extreme climatic events such as droughts, floods and cyclones (ref. X). In 2009, the cyclone names _"Fanela"_ impacted a large area of the forest in the Kirindy-Mitea National Park leaving a lot of wood fuel on the ground. This has allow uncontrolled fires to spread on large areas (~ 5000 ha) in 2013 (Fig. 1a). These fires were difficultly stopped with buckets of water and sand by the agents of the park with the help of the local people from the surrounding villages. Severe droughts in southern Madagascar in the recent years (since 2010), that could be attributed to climate-change [@Vieilledent2016], has led to famine events and can explain the migration of thousand of people in the villages of Kirindy and Lambokely which has led to an increase of the deforestation associated to slash-and-burn agriculture (Fig. 2). Moreover, the decrease of precipitation in the recent years (2010-2014), that can be associated to climate change, can have increase the frequency and magnitude of spontaneous or anthropogenic uncontrolled fires. 

#### 3.2.2 No application of conservation measures

- Political crisis in 2009, pays de non droit, état défaillant
- No means for management of protected areas and application of the laws (Fanamby, MNP)
- Conflicts of interest at the head of the state. Politics and military people have economic interests in not stopping deforestation (logging and precious wood exportation, corn crop for beer companies such as STAR, exportation of peanuts for peanut oil)  

### 3.3 Projected deforestation

```{r forest_cover, results="asis"}
forest <- forest.cover[,c(1:6)]
names(forest) <- c("Site","Area","F2000","F2010","F2014","F2050")
loss.2014 <- round(mean((forest$F2000-forest$F2014)/forest$F2000*100))
loss.2050 <- round(mean((forest$F2000-forest$F2050)/forest$F2000*100))
kable(forest)
```

Table 2: **Evolution of the forest cover with time in the Kirindy-Mitea national park (KMNP) and the Menabe-Antimena new protected area (MANAP).** _Area_: land area (in ha). _F2000_, _F2010_ and _F2014_: forest area (in ha) for the years 2000, 2010 and 2014, respectively. _F2050_: projected forest area (in ha) for the year 2050. About `r loss.2014`% of the forest have disappeared on the period 2000-2014 in the two sites and we predict the loss of around `r loss.2050`% of the forest on the period 2000-2050 for the two sites assuming a business-as-usual scenario.  

![Figure 1: **Emblematic species representative of the biodiversity of the central Menabe.** The dry forest of the central Menabe is home to a very large number of species, many of which being endemic to the region. We present here some examples of this biodiversity for different taxonomic groups: Plants, Birds, Mammals (including Lemurs), Amphibians, Reptiles. From top-left to bottom-right: 1. _Adansonia grandidieri_ (Baillon, 1888), 2. _Adansonia suarezensis_ (Perrier de la Bâthie,1952), 3. _Aglyptodactylus laticeps_ (Glaw, Vences & Böhme, 1998) 4. _Cryptoprocta ferox_ (Bennett, 1833), 5. _Falco newtoni_ (Gurney, 1863), 6. _Furcifer labordi_ (Grandidier, 1872), 7. _Hypogeomis antimena_ (Grandidier, 1869), 8. _Leptosomus discolor_ (Hermann, 1783), 9. _Mesitornis variegata_ (Geoffroy Saint-Hilaire, 1838), 10. _Microcebus berthae_ (Rasoloarison, Goodman & Ganzhorn, 2000), 11. _Mimophis mahafaliensis_, 12. _Mirza coquereli_ (Grandidier 1867), 13. _Mungotictis decemlineata_ (Grandidier 1867), 14. _Propithecus verreauxi_ (Grandidier, 1867), 15. _Pyxis planicauda_ (Grandidier 1867), 16. _Uroplatus guentheri_ (Mocquard, 1908). Sources: 1,2,5,8,10,11: authors; 3: Miguel Vences; 4,6,7,9,13,14,15,16: Wikipedia; 12: Louise Jasper.](figs/biodiversity.jpg)

![Figure 2: **Historical and forecasted deforestation in the study areas around the Kirindy-Mitea national park (KMNP) and Menabe-Antimena new protected area (MANAP).** Madagascar map is represented at the top left on panel a), with the Menabe-Antimena study area at the north and the Kinrindy-Mitea study area at the south (black rectangles). On each of the sub-panels, the boundaries of the protected areas are represented with black polygones (source: Rebioma project at http://rebioma.net). Main roads are represented with thin black lines (source: FTM BD500). Coast line is represented with a thin grey line. Belo-sur-Mer is the main village located near KMNP. Morondava and Belo-sur-Tsiribihina are the main cities located near MANAP. **a)** and **c)**: Historical deforestation on the period 2000-2010-2014 for the Menabe-Antimena and Kirindy-Mitea study areas, respectively. Green: forest cover in 2014, orange: 2000-2010 deforestation, red: 2010-2014 deforestation (source: BioSceneMada project at http://bioscenemada.net). In the Menabe-Antimena study area, the main cause of the deforestation is the slash-and-burn agriculture (_"hatsake"_) for corn and peanut crops. Most of the 2000-2014 deforestation occured around the villages of Kirindy and Lambokely. In the Kirindy-Mitea study area, the main causes of deforestation are (A) slash-and-burn agriculture, (B) cyclones followed by uncontrolled fires and (C) illegal logging. **b)** and **d)**: Projected deforestation on the period 2010-2050. Green: projected forest cover in 2050, grey: 2010-2050 deforestation. Most of the 2010-2014 deforestation observed in figure a) and c) is included in the 2010-2050 projections. Around 50% of the 2010 forest is predicted to disappear on the period 2010-2050. Most of the remaining forest will be inside the protected areas.](figs/deforestation.png)

```{r deforestation, results="asis"}
defor <- forest.cover[,c(1,7:9)]
defor.1 <- forest.cover[,c(7:9)]
defor.2 <- forest.cover[,c(10:12)]
defor[,c(2:4)] <- paste0(unlist(defor.1)," (",unlist(defor.2),"%)")
names(defor) <- c("Site","D00-10","D10-14","D10-50")
kable(defor, align=c("l","r","r","r","r"))
```

Table 3: **Evolution of the annual deforestation with time in the Kirindy-Mitea national park (KMNP) and the Menabe-Antimena new protected area (MANAP).** _D00-10_, _D10-14_ and _D10-50_: annual deforestation (in ha.yr<sup>-1</sup>) for the periods 2000-2010, 2010-2014 and 2010-2050, respectively followed by the annual deforestation rate in %.yr<sup>-1</sup>. The annual deforestation has more than doubled on the period 2010-2014 compared to the period 2000-2010. The last column of the table indicates the mean annual deforestation on the period 2010-2050 resulting from the projection of the forest cover in 2050.

![Figure 4: **Slash-and-burn agriculture (_"hatsake"_) for peanut crop around Lambokely village, Menabe-Antimena New Protected Area.** Peanut (a) is cultivated as a cash crop. Peanut production is collected and bought by dealers (b). A part of the production is at the destination of the national market but most of it is exported outside Madagascar, mainly for the Chinese market. Peanut crop is obtained through slash-and-burn agriculture (also called _"hatsake"_) and leads to the deforestation of large areas of forest near the Lambokely village, inside the delimitation of the Menabe-Antimena New Protected Area (c).](figs/arachide.jpg)

![Figure 5: **Slash-and-burn agriculture (_"hatsake"_) for corn crop.** Corn (a) is cultivated for auto-consumption and as a cash crop. Corn production is collected and bought by dealers (b). The production of corn is at the destination of the national market and is used in particular to brew beer. Corn crop is obtained through slash-and-burn agriculture (also called _"hatsake"_) and leads to the deforestation of large areas of forest in the periphery of the Kirindy-Mitea National Park (c).](figs/mais.jpg)

## 4. Discussion

### 4.1 Historical deforestation, projections and consequences (climate-change, biodiversity)

In a study analyzing the deforestation patterns in Kirindy-Ambadira Forest
Complex, @Zinner2014 found similar results to ours regarding the future deforestation. @Zinner2014 showed that half of the forest will have disappeared in 2043 in comparison to 1973 assuming a deforestation rate similar to the one over the period 1992-2010.

### 4.2 Link between deforestation and climate-change

- Drought -> spontaneous uncontrolled fires -> deforestation -> deforestation
- Climate-change -> Extreme events (cyclone) -> more wood fuel -> large uncontrolled fires
- Droughts -> starvation in southern Madagascar -> migration -> slash-and-burn agriculture -> deforestation

### 4.3 Strategies to stop deforestation

#### 4.3.1 Increasing sensibilisation

- We know conserving forest is important at the global scale to avoid carbon emissions and mitigate climate and to conserve the biodiversity and related ecosystem services.
- But we need to insist on the importance of dry forest at the local scale (effect on climate, desertification, on natural resources: wood and game, water availability)
- Sensibilisation on the risk associated to the application of the law (fines and jail)
- Women education and family planning

#### 4.3.2 Increasing repressive mesures against deforestation

- Won't be possible without a political will (_"volonté politique"_)
- Reinforcement of the institutes in charge of the protected areas and applying the conservation measures
- Application of the law banning deforestation (fines and jail)
- Possibility for the guards to draw up a report
- Help of the army
- International pressure on Malagasy government, conditionality of the international help for development
- Decreasing migration

#### 4.3.3 Development of alternatives to deforestation

- Agricultural development (compost) to increase land productivity
- Other sources of income (tourism)
- Tree plantations for wood energy and construction
- REDD+
- Most of these development approaches have failed in the past or obtained limited positive impacts. We believe that change in behaviors will be facilitated by the application of the law and the repressive measures. Population will adapt to the context of law reinforcment finding, developping and investing in new sources of income.

## Aknowledgements

This study took form during a field trip in the central Menabe (4-12th of June 2016) in the framework of the BioSceneMada project (http://bioscenemada.net). The BioSceneMada project is funded by FRB (Fondation pour la Recherche sur la Biodiversité) and the FFEM (Fond Français pour l'Environnement Mondial) under the project agreement AAP-SCEN-2013 I. We thank all the people who welcomed us and kindly provided us with useful information during our field trip, both institutional people (from DREF, MNP, WWF and Fanamby) and people from local communities (in Kirindy-Village and Lambokely particularly).

## References
