# Results

## Intensity and pattern of deforestation

```{r defor-rate_results, results="asis"}
defor <- forest.cover[,c(1,9:11)]
defor.1 <- c(as.matrix(forest.cover[,c(9:11)]))
defor.2 <- sprintf("%.2f", c(as.matrix(forest.cover[,c(14:16)])))
A <- min(as.numeric(defor.2[7:9]))
B <- max(as.numeric(defor.2[7:9]))
A_prime <- min(as.numeric(defor.2[4:6]))
B_prime <- max(as.numeric(defor.2[4:6]))
```

Deforestation rates have continuously increased since 1990 for the MANAP and KMNP study areas (Tab. \@ref(tab:defor-rate)). After a decrease in 2000--2010, deforestation in the MIKEA study area has dramatically increased in 2010--2017 (Tab. \@ref(tab:defor-rate)). We estimated that `r defor.1[7]` ha, `r defor.1[8]` ha and `r defor.1[9]` ha of forest have disappeared annually in the period 2010--2017 in the MANAP, KMNP, and MIKEA study areas, respectively. This corresponds to annual deforestation rates of `r A`--`r B`%/yr. Deforestation has more than doubled in the period 2010--2017 compared to the period 2000--2010, for which deforestation was estimated at `r A_prime`--`r B_prime`%/yr.

In the MANAP study area, large patches of deforestation associated with slash-and-burn agriculture were identified around the Kirindy and Lambokely villages and to the south of Belo-sur-Tsiribihina town (Fig. \@ref(fig:deforestation)a, label A).

In the KMNP study area, mosaic deforestation associated with slash-and-burn agriculture occurred outside the protected area, showing the relative effectiveness of the protected area to prevent deforestation in the short term (Fig. \@ref(fig:deforestation)b, label A). Much larger patches of deforestation have been observed on the two periods 2005--2010 and 2010--2015 in the east part of the protected area (Fig. \@ref(fig:deforestation)b, label B). These large patches of deforestation have been caused by the cyclone _Fanele_ that occurred in January 2009 (Appendix 2) and which was followed by uncontrolled fires. Dispersed and small-scale deforestation has also been observed in the northern and western parts of the park associated with illegal logging activities (Fig. \@ref(fig:deforestation)b, label C).

In the MIKEA study area, most of the deforestation was located in the north of the protected area (far from the Madagascar National Park office, which is located in the south of the study area) and was both due to slash and burn agriculture (Fig. \@ref(fig:deforestation)c, label A) and to uncontrolled fires following cyclone _Haruna_ which occurred in February 2013 (Fig. \@ref(fig:deforestation)c, label B; and Appendix 2).

## Deforestation drivers

### Proximate causes of deforestation: slash-and-burn agriculture and uncontrolled fires

In the MANAP study area, the main cause of deforestation was the slash-and-burn agriculture (locally known as _"hatsake"_) for maize (_Zea mays_ L.) and peanut (_Arachis hypogaea_ L.) crop (Fig. \@ref(fig:causes)). The burning of forests allows expansion of cultivable areas and optimisation of labour productivity. It provides nutrient rich ash and light for crops, increasing yields and reducing the necessary time for weeding. In the KMNP and MIKEA study areas, slash-and-burn agriculture was also identified as a cause of deforestation, but preferentially outside protected areas (Fig. \@ref(fig:deforestation)b-c, label A).
 
Inside the KMNP and MIKEA protected areas, uncontrolled fires (Fig. \@ref(fig:causes)) were the main cause of deforestation (Fig. \@ref(fig:deforestation)b-c, label B). People repeatedly set fire to former grasslands (called _"bozake"_) outside the protected area to obtain a flush of green pasture for their livestock. When uncontrolled, fires can spread across large areas of forest and cross the boundaries of the protected area. In 2009, the cyclone named _Fanele_ (Appendix 2) impacted a large area of the forest in the Kirindy-Mitea National Park leaving a lot of wood fuel on the ground. This allowed uncontrolled fires to spread throughout large areas of the park in the years following the cyclone (Fig. \@ref(fig:deforestation)b, label B). These fires were eventually stopped with water and sand by the agents of the park with the help of local villagers. The same thing happened in the MIKEA study area after cyclone _Haruna_ in 2013 (Fig. \@ref(fig:deforestation)c, label B and Appendix 2). Cyclones provide opportunities for local people to gain land on the forest. Following cyclones, it is more difficult to accuse people of destroying the forest and cyclones allow farmers to avoid the labour-intensive work of cutting down the trees before burning.

Illegal logging was also identified as a cause of forest degradation in the three study areas (Fig. \@ref(fig:deforestation)b, label C). Illegal logging is not a direct cause of deforestation but a forest without precious wood is more easily burnt than an intact forest, and so degradation usually precedes deforestation. Timber (Fig. \@ref(fig:causes)) is mainly used for house and boat construction and sold in local markets in Belo-sur-Mer and Morondava towns.

### Ultimate causes of deforestation

#### Demographic growth and migration

The population of Kirindy and Lambokely villages (Fig. \@ref(fig:deforestation)a) has been roughly multiplied by 5 between 2010 and 2015 (from about 600 to 3000 inhabitants for Kirindy and from about 1000 to 5000 for Lambokely). This increase was due both to demographic growth and migration. The demographic growth rate in Madagascar is close to 3%/yr [@Vieilledent2013] which means that the population doubles every 25 years on average. In Lambokely and Kirindy villages, the families we surveyed had all more than six children. Also, the possibility of cropping cash crops have attracted many people from the south of Madagascar during the last years, in particular from the _Androy_ and _Atsimo-Atsinanana_ regions (South-East of Madagascar). First migrants arrived in the central Menabe to work in large agricultural concessions authorized by the French colonial government. Notably, many _Tandroy_ migrants have arrived in the 1960s and established near the Beroboka village (located between Kirindy and Lambokely villages) to work in the sisal (_Agave sisalana_ Perr.) plantation of the de Heaulme family which is now abandoned. Consecutive droughts and crop failure in South-Eastern Madagascar resulted in severe famines there, that forced several thousand _Tandroy_ families to migrate to Western Madagascar in search for new farming land. Population increase in Western Madagascar has accentuated the pressures on forests. 

#### Cash crops and unregulated market

In the study areas we surveyed, peanuts (Fig. \@ref(fig:causes)) was cultivated as a cash crop. Peanuts are consumed as whole seeds or transformed into peanut oil [@MAEP2004]. According to FAOSTAT data (Tab. \@ref(tab:cropstats)), the area harvested for peanut crop in Madagascar has increased of 50% in 7 years, from 52,000 ha in 2010 to 78,426 ha in 2017. At the same time, according to UN Comtrade data, peanut exports have also dramatically increased, from 1,233 T in 2010 to 27,370 T in 2017 (Tab. \@ref(tab:cropstats) and Appendix 3). In 2017, about half of the national peanut production was exported, mainly at the destination of the Asian market (Vietnam and Pakistan, in particular). During our stay in the field in June 2016, which took place in the middle of the peanut harvest, we observed an uninterrupted parade of trucks arriving empty in the villages of Lambokely and Kirindy (Fig. \@ref(fig:deforestation)a) and leaving loaded with peanut bags.

Our surveys indicated that maize (Fig. \@ref(fig:causes)) was cultivated for auto-consumption (about 30% of the production) and as a cash crop (70%). FAOSTAT and UN Comtrade data indicate that only a small part of the national maize production was exported (about 5,000 T/yr out of a total production of about 200,000 T/yr), most part of the production being at the destination of the domestic market (Tab. \@ref(tab:cropstats) and Appendix 3). Several people we interviewed said that the maize production was sold to the Star company to brew the THB national beer. We computed that about 2,471 ha of maize are necessary to produce the annual volume of THB of 840,000 hL (Appendix 4). This is a relatively small area compared to the 249,186 ha of maize harvested annually in Madagascar (Tab. \@ref(tab:cropstats)). Other sources [@MAEP2004] indicated that maize is used for livestock (poultry and pigs) feeding in Madagascar.

Farmers we interviewed sold the peanuts and maize at the price of 1,400 MGA (Madagascar Ariary) and 400 MGA per kilogram, respectively. For 2016, the production for a household was approximately of 1.6 T of peanut and 2.5 T of maize, thus providing an annual income of about 3.24 millions MGA. Farmers we interviewed said they invested the money earned from the sale of the maize and peanut harvest in zebu herd acquisition.

#### Limits in the application of conservation policy

Since 1987 forest clearance has been illegal in Madagascar (Décret n°87-143, 20 April 1987), even outside the protected areas. 


However, as underlined by NGO in charge of the protected area management, the law is not respected nor applied. Almost nobody is prosecuted for forest clearance. Small farmers can be prosecuted as examples but are rarely incarcerated. Large landholders or those inciting small farmers to clear the forest are not prosecuted. During our stay in the field, seven people were arrested for doing slash-and-burn agriculture but were released a few days later. The political crisis of 2009, followed by several years of political instability during which funding for protected area management was severely curtailed, has reinforced this state of lawlessness. 

Several people we interviewed said that officials in the army or with political responsibilities, who are at the same time businessmen or entrepreneurs, are involved in this trade.

Moreover, authorities commonly have economic interests in not curbing deforestation as they are often involved in the trade associated with cash crops. Indeed, many politicians in Madagascar are also business leaders. Throughout the country, the Government has delegated management of the protected areas to external parties such as Fanamby and Madagascar National Parks. However, the structures in charge of the management of the protected areas have no legal enforcement powers. These powers are retained by the Malagasy Government which does not have the resources or the will to implement them adequately. Thus, the role of protected area managers is limited to raising awareness about forest conservation issues, inventorying and monitoring the biodiversity in the parks, and organizing community and NGO patrols to discourage forest clearance or report offences. They do not have the right to arrest people or to draw up a report and decide on a fine. NGOs also engage local people as conservation partners (in some cases named _"polis ny ala"_) to try to make them stewards of their forest but these have practically no power and social pressures mean that they are often unwilling to report illegal acts committed by neighbours or relatives. 

## Projected deforestation

```{r validation}
p1 <- round(perc[1,2])
p2 <- round(perc[1,3])
p3 <- round(perc[2,2])
p4 <- round(perc[2,3])
p5 <- round(perc[3,2])
p6 <- round(perc[3,3])
```

Following the conservative scenario S1 (projecting 2000--2010 mean annual deforestation) and the worst-case scenario S2 (projecting 2010--2017 mean annual deforestation), we predicted that `r loss.S1.2050`-`r loss.S2.2050`% of the forest present in 2000 will have disappeared in 2050 (Tab. \@ref(tab:forest-cover)). In the period 2000--2017, around `r loss.2017`% of the forest has already disappeared. Forest in 2050 should remain predominantly in the protected areas but deforestation is not expected to stop at the boundaries of the parks (Fig. \@ref(fig:scenarios)). The model predicted that deforestation in the future should occur close to places were deforestation occurred in the past, thus correctly simulating the contagious process of deforestation (Fig. \@ref(fig:scenarios)). Deforestation is also more likely to occur at short distances to villages and roads and at the forest edge (Fig. \@ref(fig:scenarios)). Forest fragmentation is also predicted to increase in association with deforestation (higher number of disconnected forest patches in Fig. \@ref(fig:scenarios)). Most of the deforestation observed in the period 2010--2017 was included in the deforested area predicted by the model in the period 2010--2050 (`r p1`-`r p2`% for MANAP, `r p3`-`r p4`% for KMNP, and `r p5`-`r p6`% for MIKEA for scenarios S1 and S2, respectively), thus validating partly the predictions regarding the location of the future deforestation.

\newpage
