---
title: "`r params$title`"
author: "`r params$author`"
date: "`r params$date`"
fontsize: 12pt
output:
  bookdown::gitbook:
    number_sections: yes
    split_by: chapter  
    config:
      toc:
        collapse: section
        scroll_highlight: yes
        before: null
        after: null
      toolbar:
        position: fixed
      edit: null
      download: ["pdf"]
      search: yes
      fontsettings:
        theme: white
        family: sans
        size: 2
      sharing:
        facebook: yes
        twitter: yes
        google: no
        linkedin: no
        weibo: no
        instapper: no
        vk: no
        all: ['facebook', 'google', 'twitter', 'linkedin', 'weibo', 'instapaper']
bibliography: bib/biblio.bib
biblio-style: bib/jae.bst
link-citations: yes
csl: bib/journal-of-applied-ecology.csl
---

```{r options, echo=FALSE, results="hide"}
library(bookdown)
library(knitr)
library(kableExtra)
opts_chunk$set(echo=FALSE, cache=FALSE,
               # results="hide", 
               warning=FALSE,
               message=FALSE, highlight=TRUE,
               # fig.show="hide",
			         size="small",
               fig.align="center",
               fig.pos="H",
               tidy=FALSE)
load("menabe.rda")
```

# Abstract {-}

Madagascar is recognized for both its unparalleled biodiversity and its high level of threat, associated in particular to anthropogenic deforestation. Despite the efforts to fight poverty and curb deforestation, forest cover in Madagascar is rapidly decreasing. To try to explain why it is so difficult to stop deforestation in Madagascar, we analysed further the recent deforestation process in Western Madagascar through satellite image analysis and field surveys. We show that deforestation has increased from less than 0.9%/yr on 2000--2010 to more than 2%/yr on 2010--2015. We identified two major causes of deforestation, which were not associated to agriculture for auto-consumption: slash-and-burn agriculture for the cultivation of cash crops (maize and peanut) and uncontrolled fires to open pastures. Crop production is mainly at the destination of the domestic market. In particular, maize is used for livestock feeding. The money earned by farmers is principally invested into zebu herd acquisition. Trade of agricultural commodities benefit to several intermediaries, some of who having political responsibilities. On the other hand, agents from institutions in charge of the management of the protected areas have no means to enforce law against deforestation. In the absence of an efficient strategy to stop deforestation, we predicted that 36--67% of the forest present in 2000 will have disappeared in 2050. Forest loss, apart from biodiversity loss and climate-change global issues, will be at the expense of local population. In order to stop deforestation, international aid should be used at improving local governance to enforce the environmental law and pressure should be put on trading companies to buy certified agricultural commodities not derived from deforestation.

**Keywords**: biodiversity, conservation, conflict of interest, cyclones, dry deciduous forest, fires, illegal logging, Madagascar, protected areas, slash-and-burn agriculture, tropical deforestation.

<!---
**Article statistics**:
```{r artstats, results="asis"}
Type <- c("Abstract (# words)","Main text (# words)","References","Tables","Figures")
Number <- c(265,3000,40,3,3)
artstats <- data.frame(cbind(Type,Number))
knitr::kable(artstats, align=c("r","r"), booktabs=TRUE,) %>%
  kable_styling(latex_options=c("HOLD_position","striped"), full_width=FALSE, position="center")
```
--->

**Target journals** (selection, 2015 IF): _Conservation Letters_ (7.126), _Conservation Biology_ (4.257), _Environmental Research Letters_ (4.134), _Biological Conservation_ (3.985), _Ambio_ (2.555), _Environmental Conservation_ (2.235), _Biotropica_ (1.944), _Tropical Conservation Science_ (1.55), _People and Nature_.

\newpage