---
title: "`r params$title`"
author: "`r params$author`"
date: "`r params$date`"
fontsize: 12pt
output:
  bookdown::gitbook:
    number_sections: yes
    split_by: chapter  
    config:
      toc:
        collapse: section
        scroll_highlight: yes
        before: null
        after: null
      toolbar:
        position: fixed
      edit: null
      download: ["pdf"]
      search: yes
      fontsettings:
        theme: white
        family: sans
        size: 2
      sharing:
        facebook: yes
        twitter: yes
        google: no
        linkedin: no
        weibo: no
        instapper: no
        vk: no
        all: ['facebook', 'google', 'twitter', 'linkedin', 'weibo', 'instapaper']
bibliography: bib/biblio.bib
biblio-style: bib/jae.bst
link-citations: yes
csl: bib/journal-of-applied-ecology.csl
---

```{r options, echo=FALSE, results="hide"}
library(bookdown)
library(knitr)
library(kableExtra)
opts_chunk$set(echo=FALSE, cache=FALSE,
               # results="hide", 
               warning=FALSE,
               message=FALSE, highlight=TRUE,
               # fig.show="hide",
			         size="small",
               fig.align="center",
               fig.pos="H",
               tidy=FALSE)
load("menabe.rda")
```

```{r loss, results="hide"}
forest <- forest.cover[,c(1:8)]
names(forest) <- c("Site","Area","F1990","F2000","F2010","F2017","F2050,S1","F2050,S2")
loss.2017 <- round(mean((forest$F2000-forest$F2017)/forest$F2000*100))
loss.S1.2050 <- round(mean((forest$F2000-forest[,"F2050,S1"])/forest$F2000*100))
loss.S2.2050 <- round(mean((forest$F2000-forest[,"F2050,S2"])/forest$F2000*100))
```

# Abstract {-}

Madagascar is recognized both for its unparalleled biodiversity and the high level of threat suffered by this biodiversity, associated in particular with anthropogenic deforestation. Despite sustained efforts to fight poverty and curb deforestation, forest cover in Madagascar is rapidly decreasing. To try to explain why it is so difficult to stop deforestation in Madagascar, we analysed the recent deforestation process in Western Madagascar through satellite image analysis and field surveys. We show that deforestation has increased from less than 0.9%/yr on 2000--2010 to more than 2%/yr on 2010--2017. We identified two major causes of deforestation, which were not associated with subsistence agriculture: slash-and-burn agriculture for the cultivation of cash crops (maize and peanut), and uncontrolled fires to create open pasture. Maize production is mainly at the destination of the domestic market and is used in particular for livestock feeding. Peanut production has boomed since 2013 and more than half of it is now exported towards asiatic countries. The money earned by farmers is principally invested into zebu herd acquisition. Trade of agricultural commodities benefits several intermediaries, some of whom have political responsibilities thus creating conflicts of interest. On the other hand, agents from institutions in charge of the management of the protected areas have no means to enforce laws against deforestation. In the absence of an efficient strategy to stop deforestation, we predicted that `r loss.S1.2050`-`r loss.S2.2050`% of the forest present in 2000 will have disappeared in 2050. Forest loss, apart from biodiversity loss and climate-change global issues, will be at the expense of local population. In order to stop deforestation, international aid should be used to improve local governance to enforce environmental laws and pressure should be put on trading companies to buy certified agricultural commodities that are not derived from deforestation.

**Keywords**: biodiversity, conservation, conflict of interest, cyclones, dry deciduous forest, fires, illegal logging, Madagascar, protected areas, slash-and-burn agriculture, tropical deforestation.

<!---
**Article statistics**:
```{r artstats, results="asis"}
Type <- c("Abstract (# words)","Main text (# words)","References","Tables","Figures")
Number <- c(265,3000,40,3,3)
artstats <- data.frame(cbind(Type,Number))
knitr::kable(artstats, align=c("r","r"), booktabs=TRUE,) %>%
  kable_styling(latex_options=c("HOLD_position","striped"), full_width=FALSE, position="center")
```
--->

**Target journals** (selection, 2015 IF): _Conservation Letters_ (7.126), _Conservation Biology_ (4.257), _Environmental Research Letters_ (4.134), _Biological Conservation_ (3.985), _Ambio_ (2.555), _Environmental Conservation_ (2.235), _Biotropica_ (1.944), _Tropical Conservation Science_ (1.55), _People and Nature_.

\newpage